---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
  \usepackage{xeCJK}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
options(font_family = NULL)
```

# Tasks summary

## Overview

\includegraphics[height=65mm]{./figs/orders_11-12.pdf}

## Methods used

\includegraphics[height=65mm]{./figs/workflow2_11-12.pdf}

## New Methods

- edqtl: GTEX (eQTL, edQTL)
- biblio: bibliometrix
- hybrid: miRNA binding RNA
- miranda: miRNA binding mRNA
- tcmsp: TCM Database
- pubchemr: Compounds ID mapping
- swiss: Batch prediction
- biomart2: Biomart API mapping genes

```{r}
writeLines(news)
NULL
```

# Article sharing

## RNA velocity

\includegraphics[height=50mm]{~/Pictures/Screenshots/Screenshot from 2024-01-11 10-08-54.png}

```{r eval = T, echo = F, results = "asis"}
citethis("RnaVelocityOfLaMan2018")
```

## Details

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-01-11 10-13-21.png}

## Compare with Pseudotime analysis

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-01-11 10-15-06.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/embryo_pr_graph_by_time.png}
:::

::::::

## Recent years: cellDancer and PhyloVelo 

```{r}
rsvg::rsvg_png("~/Pictures/diagram_no_text.svg", "~/Pictures/diagram_no_text.png", 4000, 4000)
```

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=50mm]{~/Pictures/about6.png}
:::

::: {.col data-latex="{0.1\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/diagram_no_text.png}
:::

::::::

# Schedule

## Workflow document

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-01-11 10-39-38.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-01-11 10-41-21.png}
:::

::::::

# Thanks

```{r}
alls <- get_orders()
these <- filter(alls, grpl(belong, "2023-1[12]"))

p.lst <- plot_orders_summary(these)
p.lst$p.alls
autosv(p.lst$p.alls, "orders_11-12")

p.wlst <- plot_workflow_summary(these)
p.wlst$p.fr2
autosv(p.wlst$p.fr2, "workflow2_11-12")
```

```{r}
news <- get_workflow_news("2023-11-01", "2023-12-01")
```
