---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
  \usepackage{xeCJK}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
options(font_family = NULL)
```

# Tasks summary

## Overview 2024-03

\includegraphics[height=65mm]{./figs/workflow2_03.pdf}

## New Methods

- unitmp: UNIfied database of TransMembrane Proteins
- prr: (RNA-seq) Clinical Chemotherapeutic Response 
- musite (GPS-MSP, PRmePred): (MusiteDeep) Post-translational modification site
    - Web
    - Python
- epifactor: Epigenetic regulators

```{r}
writeLines(news)
```

# Article sharing

## Concept

- WGS / WES
- GWAS
- Gene locus  (基因座)
- Allele (等位基因) 
- Linkage Disequilibrium  (连锁不平衡) 
- ...
- eQTL (GTEX database): SNPs $\Rightarrow$ mRNA expression levels

## GWAS

- Disease $\rightleftarrows$ Variants
- Variants $\Rightarrow$ Genes
- Variants $\Rightarrow$ ... $\Rightarrow$ Genes

\qquad \qquad $\Downarrow$

- Variants $\Rightarrow$ ? $\Rightarrow$ Disease

## Article with multiple tools

\includegraphics[width=135mm]{~/Pictures/Screenshots/Screenshot from 2024-04-11 15-16-33.png}

## Flow Chart

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
- Sherlock
- SMR
- NetWAS (GIANT websevier)
- Depict
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-04-11 15-15-07.png}
:::

::::::


## Sherlock (and SMR) \small via eQTL

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-04-11 15-29-02.png}

## Depict \small via Prediction

:::::: {.cols data-latex=""} 
::: {.col data-latex="{0.4\textwidth}"} 
1. 预测关联位点对应基因的功能
2. 候选基因功能富集分析
3. 候选基因表达特异性分析 (细胞、组织)
4. Gene prioritization
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-04-11 15-39-17.png}
:::
::::::


# Schedule

## Schedule

- Finish orders
- New methods

# Thanks

```{r}
alls <- get_orders()
these <- dplyr::filter(alls, grpl(belong, "2024-03"))

p.wlst <- plot_workflow_summary(these)
p.wlst$p.fr2
autosv(p.wlst$p.fr2, "workflow2_03")
```

```{r}
news <- get_workflow_news("2024-03-01")
writeLines(news)
```
