---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
```

## Last Month

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
- AutoDock (vina)
    - Computational
- Weighted genes co-expression
- RNA-protein binding prediction
- Prediction model
:::

::: {.col data-latex="{0.5\textwidth}"} 
- Single-cell analysis
    - Standard processing (Seurat)
    - Cell annotation (Garnett)
    - Cell communication (CellChat)
    - Cell pseudo-time (monocle3)
:::
::::::

# Repetition of Technology

## Article

\includegraphics[width=135mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 16-33-47.png}

```{r eval = T, echo = F, results = "asis"}
citethis("SingleCellTraHeLe2022")
```

## Research idea

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 

- CRD and disease (Malignant)
    - Clustering
    - Cell annotation
    - WGCNA
- CRD and therapy
    - ...
    - Pathway enrichment
- CRDscore validation
    - Correlation

:::


::: {.col data-latex="{0.5\textwidth}"} 
- CRD and prognosis
    - TCGA Survival
    - TCGA CRDscore
- Construct prediction model
    - LASSO
    - SVM
- Experimental validation
:::

::::::

## Techniques 1

Standard worflow and annotation

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-17-19.png}

## Techniques 2

Weighted gene co-expression ... (WGCNA)

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-19-12.png}


## Techniques 3

Differential analysis and Pathway enrichment

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-30-36.png}


## Techniques 4

Cell–cell ligand‐receptor (LRs) analysis

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-34-07.png}


## Techniques 5

Survival analysis

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-36-16.png}


## Techniques 6

LASSO and SVM

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-43-28.png}

## Techniques 7

\includegraphics[height=55mm]{~/Pictures/Screenshots/Screenshot from 2023-08-08 17-47-10.png}

# Thank you


