---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
  \usepackage{xeCJK}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
options(font_family = NULL)
```

# Tasks summary

## Overview 2024-01 ~ 2024-02

\includegraphics[height=65mm]{./figs/workflow2_01-02.pdf}

## New Methods

- gmix: `DisGeNet`, `GeneCards`, `PharmGKB`
- lzerd: `LZerD` and `HawkDock` webservers, protein–protein docking
- hob: Python, human oral bioavailability
- plantdb: (crawler) The Database `PlantaeDB`
- superpred: (crawler) drug-targets relationship prediction (SwissTargetPrediction)
- ocr: Python, `doctr`
- tfbs: (crawler) Transcription Factor Target Gene Database

## New Methods

- mpa: `MetaPhlAn`, microbial communities from metagenomic data
- adcp: auto molecular docking (docking peptides)
- nomo: logistic, nomogram
- classyfire: systematic classification of chemical compounds
- msconvert: file formats of MASS data
- xcms: MASS data preprocessing

```{r}
writeLines(news)
```

# Article sharing

## Reconstruction of colon cancer microbiome

\includegraphics[height=50mm]{~/Pictures/Screenshots/Screenshot from 2024-03-12 16-23-47.png}

## Details

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.45\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-03-12 16-25-37.png}
:::

::: {.col data-latex="{0.45\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2024-03-12 16-49-27.png}
:::

::::::

## Code availability

\includegraphics[width=135mm]{~/Pictures/Screenshots/Screenshot from 2024-03-12 16-30-58.png}

# Schedule

## Schedule

- Finish orders
- New methods

# Thanks

```{r}
alls <- get_orders()
these <- dplyr::filter(alls, grpl(belong, "2024-0[12]"))
these <- dplyr::filter(these, id != "workflow")

p.lst <- plot_orders_summary(these)
p.lst$p.alls
autosv(p.lst$p.alls, "orders_01-02")

p.wlst <- plot_workflow_summary(these)
p.wlst$p.fr2
autosv(p.wlst$p.fr2, "workflow2_01-02")
```

```{r}
news <- get_workflow_news("2024-01-01", "2024-02-01")
writeLines(news)

```
