---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
```

# Repetition of Technology

## Article

\includegraphics[width=135mm]{~/Pictures/Screenshots/Screenshot from 2023-07-11 10-24-38.png}

```{r eval = T, echo = F, results = "asis"}
citethis("SerumAndUrineYang2017")
```

## Research idea

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.3\textwidth}"} 
- Main
    - Identification
    - Quantification
    - Feature selection
    - Establish model
    - Validation
:::

::: {.col data-latex="{0.6\textwidth}"} 
\includegraphics[height=65mm]{./figs/idea.pdf}
:::

::::::

```{r}
idea <- as_network(
  list(
    "Data:Metadata, Serum, Urine",
    "Metadata:Statistic",
    "Urine:Analysis.",
    "Analysis.:Top_metabolites",
    "Serum:Identification, Quantification",
    "Identification:H-NMR",
    "Quantification:Screening",
    "Screening:PCA, OPLS-DA, Correlation",
    "OPLS-DA:Top_metabolites",
    "Top_metabolites:Pathway, Random_forest, Logistic",
    "Logistic:ROC"
  )
)
p <- flowChart(idea, 1.1, 1.02)
smallsvg(p, "idea.pdf", 9, 6)
```

## Statistic of metadata

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
- The pre-test
    1. Normal distribution
       - `shapiro.test()`
    2. Variance test
       - `bartlett.test()`
- ANOVA
    - `aov()`
- Multiple comparison
    - `TurkeyHSD()`
:::

::: {.col data-latex="{0.6\textwidth}"} 

\includegraphics[height=65mm]{./figs/idea_ex.pdf}

:::

::::::

```{r}
idea_ex <- as_network(
  list(
    "Metadata:Statistic",
    "Statistic:Normal, Non-normal",
    "Non-normal:Likeli-hood_ratio_Test",
    "Normal:Variance., T-test",
    "Variance.:ANOVA",
    "ANOVA:Fisher LSD, Tukey HSD"
  )
)
p <- flowChart(idea_ex, , 1.01)
smallsvg(p, "idea_ex.pdf", 6.5, 5)
```

## Demo statistic

```{r}
data <- openxlsx::read.xlsx("./jcsm12246-sup-0002-meta-of-tables-4.xlsx",
  startRow = 2, sheet = 2)
data <- dplyr::select(data, Number, Stage, Total.cholesterol)
demo <- split_lapply_rbind(data, ~ Stage, head, n = 5)
demo <- dplyr::rename(demo, sample = Number, group = Stage)
```

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 

```{r eval = T, echo = F}
knitr::kable(head(demo, n = 13), caption = "Demo data")
```

:::

::: {.col data-latex="{0.5\textwidth}"} 

```{r}
metadata <- dplyr::distinct(demo, sample, group)
demo.long <- handling_na.long(demo)
res.lsd <- dplyr::filter(variance_analysis(demo.long), type != "Tukey HSD")
```

```{r}
fun <- function(data) {
  p <- ggplot(data) +
    geom_col(aes(x = name, y = p.value, fill = p.value)) +
    coord_flip() +
    scale_fill_gradient2(mid = "lightyellow", high = "red", midpoint = 0.05) +
    facet_wrap(~ factor(type, unique(type)), ncol = 1, scales = "free_y")
}
res.vis <- fun(all.p)
smallsvg(res.vis, "var_p.pdf", 7, 7)
```

\includegraphics[height=62mm]{./figs/var_p.pdf}

:::

::::::

## Multivariate statistics: PCA

```{r}
iris.show <- split_lapply_rbind(iris, ~ Species, head, n = 4)
```

```{r}
data <- dplyr::mutate(iris, sample = paste0("sample", 1:nrow(iris)))
data <- dplyr::rename(data, group = Species)
data <- pca_data.long(data)
```

```{r}
p <- ggplot(data$data, aes(x = PC1, y = PC2, fill = group)) +
  geom_point(alpha = 0.8, size = 3, shape = 21, stroke = 0, color = "transparent") +
  stat_ellipse(aes(color = group), level  =  0.95) +
  labs(x = paste0("PC1 (", anno[1], ")"),
    y = paste0("PC2 (", anno[2], ")"), color = "Group", fill = "Group") +
  ggsci::scale_color_npg() +
  ggsci::scale_fill_npg() +
  theme()
smallsvg(p, "pca.pdf", 5, 5)
```

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.6\textwidth}"} 

```{r eval = T, echo = F}
knitr::kable(iris.show, caption = "Demo data")
```

:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=60mm]{./figs/pca.pdf}
:::

::::::

## Multivariate statistics: OPLS-DA

```{r}
whi <- which(metadata$group %in% c("virginica", "setosa"))
data <- data.frame(t(data.form))
data <- dplyr::slice(data, whi)
pdf("figs/opls_form.pdf", 7, 7)
metadata.opls <- dplyr::slice(metadata, whi)
opls <- ropls::opls(
  data, as.character(metadata.opls$group),
  predI = 1, orthoI = NA
)
dev.off()
```

```{r}
res <- cbind(opls@scoreMN[, 1], opls@orthoScoreMN[, 1])
colnames(res) <- c("h1", paste0("o", 1))
# vip <- data.frame(opls@vipVn)
# vip <- cbind(rownames(vip), vip)
# colnames(vip) <- c("var", "vip")
```

```{r}
x_lab <- paste0("T score[1](", opls@modelDF[1, "R2X"] * 100, "%)")
y_lab <- paste0("Orthogonal T score[1](", opls@modelDF[2, "R2X"] * 100, "%)")
p <- ggplot(data.frame(res), aes(x = h1, y = o1)) +
 	geom_point(alpha = 0.8, size = 3, shape = 21,
    aes(fill = metadata.opls$group), stroke = 0, color = "transparent") +
 	stat_ellipse(aes(color = metadata.opls$group), level  =  0.95) +
  ggsci::scale_color_npg() +
  ggsci::scale_fill_npg() +
  labs(x = x_lab, y = y_lab, color = "Group", fill = "Group")
smallsvg(p, "opls.pdf", 5, 4)
```

:::::: {.cols data-latex=""} 
::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{./figs/opls_form.pdf}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{./figs/opls.pdf}
:::
::::::

## Random Forest

```{r}
set.seed(71)
iris.rf <- randomForest::randomForest(Species ~ ., data=iris, importance=TRUE, proximity=TRUE)
data <- round(randomForest::importance(iris.rf), 2)
data <- data.frame(data)
data <- dplyr::mutate(data, var = rownames(data))
```

```{r}
p <- ggplot(data) +
    geom_col(aes(x = reorder(var, MeanDecreaseAccuracy),
        y = MeanDecreaseAccuracy, fill = MeanDecreaseAccuracy), width = .7) +
    labs(x = "Variable", y = "") +
    coord_flip()
smallsvg(p, "rf.pdf", 7, 7)
```

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.6\textwidth}"} 

```{r eval = T, echo = F}
knitr::kable(head(iris.show, n = 13), caption = "Traning data")
```

:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{./figs/rf.pdf}
:::

::::::

## Logistic regression

```{r}
iris_m <- dplyr::mutate(iris, Species = sample(c(0, 1), nrow(iris), T))
model <- glm(Species ~ Sepal.Length + Sepal.Width + Petal.Length + Petal.Width, data = iris_m, family = "binomial")
fun <- function(x) rnorm(nrow(iris), mean(x), mean(x) / 10)
set.seed(10)
iris_v <- dplyr::mutate(iris,
   Sepal.Length = fun(Sepal.Length),
   Sepal.Width = fun(Sepal.Width),
   Petal.Length = fun(Petal.Length),
   Petal.Width = fun(Petal.Width),
   Species = NULL
)
pos <- predict(model, iris_v, type = "response")
```

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 

```{r eval = T, echo = F}
knitr::kable(head(iris.show, n = 4), caption = "Traning data")
```

```{r eval = T, echo = F}
knitr::kable(head(round(iris_v, 2), n = 4), caption = "Validate data")
```

:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=65mm]{./figs/roc.png}
:::

::::::


# Thank you
