---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
```

# Last Month

## Order 1: TNA and Sepsis

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.25\textwidth}"} 
- Screen DEGs
- Microbiota
- Ferroptosis
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.3\textwidth}"} 
\includegraphics[height=45mm]{~/outline/lixiao/2023_10_05_xiaguolian/Figure+Table/Target-genes-of-TNA-in-mutiple-tissue-of-sepsis-of-Hippo-pathway.pdf}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.4\textwidth}"} 
\includegraphics[height=45mm]{~/outline/lixiao/2023_10_05_xiaguolian/Figure+Table/All-DEGs-of-GSEA-enrichment-via-FerrDb-V2.pdf}
:::

::::::

## Order 2: Spatial scRNA

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
- Cell annotation
- Cancer cell prediction
- Cancer cell subtype
- Cell communication
- ...
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.6\textwidth}"} 
\includegraphics[height=35mm]{~/outline/lixiao/2023_10_06_lunST/Figure+Table/cancer-subtypes-in-all-cells.pdf}
\includegraphics[height=20mm]{~/outline/lixiao/2023_10_06_lunST/Figure+Table/visualization-of-communication-between-macrophage-and-cancer-cells.pdf}
:::

::::::


## Order 3: CKD and Renal Cancer

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.2\textwidth}"} 
- RCC
- CKD
    - HN
    - IgA
    - IMN
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.3\textwidth}"} 
\includegraphics[height=60mm]{~/outline/lixiao/2023_09_27_dualdisease/Figure+Table/fig1.pdf}
:::

::: {.col data-latex="{0.1\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.45\textwidth}"} 
\includegraphics[width=60mm]{~/outline/lixiao/2023_09_27_dualdisease/Figure+Table/fig3.pdf}
:::

::::::

# Article Sharing

## Article

\includegraphics[height=50mm]{~/Pictures/Screenshots/Screenshot from 2023-11-09 17-41-15.png}

```{r eval = T, echo = F, results = "asis"}
citethis("RnaEditingUndLiQi2022")
```

## A molecular cell atlas of the human lung

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
- RNA editing
    - A-to-I editing (mostly)
    - C-to-U editing
- eQTLs
- edQTLs
- sQTLs
- ...
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.6\textwidth}"} 
\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-11-09 17-52-24.png}
:::

::::::

## edQTLs data in GTEx database

\includegraphics[width=130mm]{~/Pictures/Screenshots/Screenshot from 2023-11-09 17-58-44.png}

# Issues

## Issues

1. Meta-analysis: Literatures

# Schedule

## Projects

- RNA-seq and GPBAR/TGR5
- RNA-editing and inflammation
- ...

