---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
```

# Last Month

## Order 1: WES (mutation detection)

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.4\textwidth}"} 
- QC
- Detect variants
- filter variants
- Annotation
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{~/outline/lixiao/2023_08_17_eval/Figure+Table/summary-of-mutations-in-samples.pdf}
:::

::::::

## Order 2: Multi-Omics

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
- Network pharm.
- Omics: Microbiota (16s RNA)
- Omics: Metabolites
- Microbiota $\Rightarrow$ Metabolites: gutMDisorder
- Omics: RNA
- drug Binding: Molecular docking
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=65mm]{~/outline/lixiao/2023_08_24_eval/Figure+Table/Integration-of-datasets-for-metabolites-and-microbiota-selection.pdf}
:::

::::::

## Order 3: Package touchPDB

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
- Protein basic Information
- Active sites
- Binding sites
- Visualization
- ...
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-19 10-14-19.png}
:::

::::::

## Order 4: dual disease and pathway selection

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.3\textwidth}"} 
- Multi datasets
    - TCGA
    - GEO
- WGCNA
- Enrichment
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[height=60mm]{~/outline/lixiao/2023_07_20_yuye/Figure+Table/fig4.pdf}
:::

::::::

# Article Sharing

## Article

\includegraphics[width=135mm]{~/Pictures/Screenshots/Screenshot from 2023-10-11 17-53-11.png}

```{r eval = T, echo = F, results = "asis"}
citethis("AMolecularCelTravag2020")
```

## A molecular cell atlas of the human lung

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-10-11 17-55-18.png}

## Marker identification

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-10-11 17-57-09.png}

## Usefull and available data

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-10-11 18-00-27.png}

# Issues

## Issues

1. No public available data
2. No correlation between multi-omics
3. Computation is time-consumed

# Schedule

## Projects

- Gene selection: XiaGuoLian
- Spatial transcriptome: CaoZhuo
- ...
- Dual disease correlation: KIRC and CKD 
- Image repeat detection


