---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    latex_engine: xelatex
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
  \usepackage{xeCJK}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
options(font_family = NULL)
```

# Tasks summary

## Overview

\includegraphics[height=65mm]{./figs/orders.pdf}

# Workflow summary

## Structure \small Automatic data arrangement 

\includegraphics[height=65mm]{./figs/workflow1.pdf}

## Overview \small Frequency

\includegraphics[height=65mm]{./figs/workflow2.pdf}

# Report summary

## Structure \small Automatic annotation

\includegraphics[height=62mm]{./figs/report1.pdf}

# System summary

## Overview \small Automatic summary

\includegraphics[height=65mm]{./figs/system1.pdf}

# Summary

## Prospect

- More workflow
- More details in report
    - Method description
    - Figure description
    - Table description
- More intelligent system

# Thanks

```{r}
alls <- get_orders()
alls <- filter(alls, !grpl(belong, "12-01$"))

p.lst <- plot_orders_summary(alls)
p.lst$p.alls
autosv(p.lst$p.alls, "orders")

p.wlst <- plot_workflow_summary(alls)
p.wlst$p.fr1
p.wlst$p.fr2
autosv(p.wlst$p.fr1, "workflow1")
autosv(p.wlst$p.fr2, "workflow2")

p.rep <- plot_report_summary()
p.rep
autosv(p.rep, "report1")

p.task <- plot_task_summary()
p.task$p.alls
autosv(p.task$p.alls, "system1")
```
