---
title: 'Seminar'
author: |
        | Lichuang Huang
institute: Wie-Biotech
date: '`r format(Sys.Date() + 1)`'
output:
  beamer_presentation:
    keep_tex: true
    df_print: kable
    theme: "Berlin"
    colortheme: "beaver"
    fonttheme: "structurebold"
    includes:
      in_header: ./templ_beamer_company.tex
fontsize: 5pt
header-includes:
  \AtBeginEnvironment{longtable}{\tiny}
  \titlegraphic{\centering \includegraphics{./logo_lixiao.png}}
  \usepackage{caption}
  \captionsetup{font={tiny}}
  \usepackage{setspace}
  \setstretch{1.3}
  \linespread{1.3}
---

```{r setup, include = F}
knitr::opts_chunk$set(echo = F, eval = F, message = F)
if (!requireNamespace("utils.tool"))
  devtools::load_all("~/utils.tool/")
```

# Last Month

## 16s rRNA

Qiime2 and MicrobiotaProcess.

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 

- importing data
- ...
- Alpha and beta diversity analysis
- Alpha rarefaction plotting
- Taxonomic analysis
- ...

:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=70mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-30-40.png}
:::

::::::

## 16s rRNA

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-37-52.png}

\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-36-20.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-39-34.png}
:::

::::::

## 16s rRNA

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-41-59.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-43-19.png}
:::

::::::

## WES

~~GATK4~~ elprep, ANNOVAR and maftools 

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-54-56.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 16-50-51.png}
:::

::::::

## WES

:::::: {.cols data-latex=""} 

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-00-41.png}
:::

::: {.col data-latex="{0.02\textwidth}"}
\hspace{1pt}
:::

::: {.col data-latex="{0.5\textwidth}"} 
\includegraphics[width=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-01-38.png}
:::

::::::

# Repetition of Technology

## Article

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-43-53.png}

```{r eval = T, echo = F, results = "asis"}
citethis("BugsigdbCapturGeistl2023")
```

## A wide range of data sources

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-42-21.png}

## Microbe co-occurrence

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-55-32.png}

## Microorganisms and disease

\includegraphics[height=65mm]{~/Pictures/Screenshots/Screenshot from 2023-09-12 17-50-28.png}

